---
title: "ESDprojectNo.1"
author: "Jaeyuel Park"
date: '2020 9 1 '
output: html_document
---
## Get the data

Download file from the following [link](https://d396qusza40orc.cloudfront.net/exdata%2Fdata%2Fhousehold_power_consumption.zip)


## Data Processing
```{r read, echo = TRUE}
dat <- read.table("household_power_consumption.txt",sep = ";", header = TRUE)
```

First, need to see how data is composed
```{r skimming through data,echo = TRUE}
head(dat)
summary(dat)
```

 By doing so, we could see that the date and time are not in POSXICT, but character. So we need to put a little bit of change here using lubridate package. Also we need to change character into numerics for other columns.
 
```{r transforming data, echo= TRUE}
library(lubridate)
dat$Date<-dmy(dat$Date)
class(dat$Date)
```

 Now as mentioned in the readme of the assignment, we only need data from the dates 2007-02-01 and 2007-02-02. So it would be easier if we subset the data.
 
```{r subsetting data, echo = TRUE}
dat1 <- subset(dat, Date == "2007-02-01"| Date == "2007-02-02")
for (i in 3:9){
  dat1[,i] <- as.numeric(dat1[,i])
}
```
 
 
## Building figures

# figure 1

 We could see that it's histogram with Global Active Power on x-axis with the title "Global Active Power"

```{r figure1, echo = TRUE}
hist(dat1$Global_active_power, main= "Global Active Power", xlab= "Global Active Power(kilowatts)",col = "red")
```

# figure 2

 We need to create another column, date and time merged. 
```{r Datetime, echo = TRUE}
dat1$Datetime <- ymd_hms(paste(dat1$Date, dat1$Time))
```
 Now we could create a figure.

```{r figure2, echo = TRUE}
with(dat1, plot(Datetime, Global_active_power, type = "l", xlab = "", ylab = "Global Active Power(kilowatts)"))
```

# figure 3

```{r figure3, echo = TRUE}
with(dat1, plot(Datetime, Sub_metering_1, type = 'l',xlab = "",ylab = "Energy sub metering"))
lines(Sub_metering_2~Datetime, dat1, col = "red")
lines(Sub_metering_3~Datetime, dat1, col = "blue")
legend("topright", col = c("black", "red", "blue"), lwd=2 ,legend = c("Sub_metering_1","Sub_metering_2","Sub_metering_3"))
```

#figure 4

```{r figure4, echo = TRUE}
par(mfrow =c(2,2))
with(dat1, plot(Datetime, Global_active_power, type= 'l'))
with(dat1, plot(Datetime, Voltage, type= 'l'))
with(dat1, plot(Datetime, Sub_metering_1, type = 'l',xlab = "",ylab = "Energy sub metering"))
lines(Sub_metering_2~Datetime, dat1, col = "red")
lines(Sub_metering_3~Datetime, dat1, col = "blue")
legend("topright", col = c("black", "red", "blue"), lty =1, cex = 0.5 ,lwd=2 , bty = "n", legend = c("Sub_metering_1","Sub_metering_2","Sub_metering_3"))
with(dat1, plot(Datetime, Global_reactive_power, type = 'l'))
```

```